### 2024-03-13 README.Rmd
update core platform prep plot
delete unneeded figures

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Diverse lithic production strategies in southwest China during Late Middle Pleistocene"
```

# Diverse lithic production strategies in southwest China during Late Middle Pleistocene

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/benmarwick/lithicprodswchinalatemiddlepleistocene/master?urlpath=rstudio)

@@

Our pre-print is online here:

> Yue Hu, Ben Marwick, (nd). _`r Title`_. , Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

  - [:file\_folder: paper](/analysis/paper): R Markdown source document
    for manuscript. Includes code to reproduce the figures and tables
    generated by the analysis. It also has a rendered version,
    `paper.docx`, suitable for reading (the code is replaced by figures
    and tables in this file)
  - [:file\_folder: data](/analysis/data): Data used in the analysis.
  - [:file\_folder: figures](/analysis/figures): Plots and other
    illustrations

>>>>

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Late Middle Pleistocene lithic technology at Guanyindong cave, Southwest China: Diversity and innovation during the Chinese Middle Palaeolithic"
```

# Late Middle Pleistocene lithic technology at Guanyindong cave, Southwest China: Diversity and innovation during the Chinese Middle Palaeolithic

@@

@@

  - [:file\_folder: paper](/analysis/paper): R Markdown source document
    for our manuscript. It also has a rendered version,
    `paper.docx`, suitable for reading (the code is replaced by figures
    and tables in this file)
  - [:file\_folder: data](/analysis/data): Data used in the analysis. 
  - [:file\_folder: figures](/analysis/figures): Plots and other
    illustrations
